### 2018-07-22 express2018/related.tex
Fixed 'It is not very clear which things are novel (comparing with Nesi)' #42 (addition changes)

\hl{Monica Nesi made the first CCS formalisations for both pure and
value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
theorem prover.\footnote{Part of 
 her scripts is at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
Her main focus was on implementing decision procedures (as ML functions) for
automatically proving bisimilarities of CCS
processes, thus she stopped proving deeper theorems in Milner's book, once the congruence and algebraic laws of
strong, weak and rooted bisimilarity were proved. \hl{\textbf{Her work is
  the working basis for ours.} However, now the
differences are substantial, especially in the way of defining
bisimilarities. We have benefited from recent versions of HOL4, and our current
formalisation has covered a much larger spectrum of the whole theory.}

>>>>

\hl{Monica Nesi made the first CCS formalisations for both pure and
value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
theorem prover.\footnote{Part of 
 her scripts is at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
Her main focus was on implementing decision procedures (as ML functions) for
automatically proving bisimilarities of CCS
processes, thus she stopped proving deeper theorems in Milner's book, once the congruence and algebraic laws of
strong, weak and rooted bisimilarity were proved. \hl{Her work is
  the working basis of ours. However, the differences are substantial, especially in the way of defining
bisimilarities. We greatly benefited from features and standard
libraries in recent versions of HOL4, and our formalisation has
covered a much larger spectrum of the whole theory.}
